### 2020-03-02 draft_ABP.tex
update

The $\mathcal I(\mathbf X,\{c\})$ is convergent when $\mathbf X$ is contained inside
the Minkowski sum $\mathcal P=\sum_I c_I \mathcal P_I$ of Newton polytopes 
$\mathcal P_I=\mathbf N[p_I]$. For a facet $F_a$ of $\mathcal P$, this condition 
requires that $\mathbf X$ should lay on one side of $F_a$ which is equivalent to 
an inequality of variables $\mathbf S=(-X_1,\dots,-X_d,c_1,\dots,c_m)$, 
$W_a^JS_J\geq 0$, where $W_a^J$ is determined by the facet $F_a$. 
These inequalities cut out a polyhedron in the $(d+m)$-dimensional space of $\mathbf S$,
which is called the \textit{big polyhedron} of $\mathcal P$, 
and the integral $\mathcal I(\mathbf S)$ converges for each point $\mathbf S$ 
inside this polyhedron.

Dually, we can describe the big polyhedron by its vertices. Suppose 
$\{V_J^A\}_{1\leq A\leq v}$ are its non-zero vertices, the point $\mathbf S$ inside 
the polyhedron can be written as $S_J = U_A V^A_J$ with non-nagetive coefficients 
$\{U_A\}_{1\leq A\leq v}$.  Therefore, the integral $\mathcal I(\mathbf S)$
can be seen as a function of `dual coordinates' $\{U_A\}$ which encourages us to 
rewrite the integral to make it manifest by
\[
	\mathcal I(U)=
	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
	\prod_{J}p_J^{-\alpha' S_J}
	=
	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
	\prod_{A}u_A^{\alpha' U_A},
\]
where we introduce a new set of variables $u_A = \prod_J p_J^{-V_J^A}$ for 
$A=1,\dots,v$. Note that there's no unique way to write $S_J=U_AV_J^A$ when
the big polyhedron is not a simplex, \textit{i.e.} $v>d+m$, and in this case,
$u$-variables $\{u_A\}$ are not independent. 
When the big polyhdron is a simplex, \textit{i.e.} $N=v=d+m$, where $N$ is 
the number of facets of the big polyhdron or the original polytope $\mathcal P$,
and inequalities $U_A=S_J(V^{-1})^J_A\geq 0$ are exactly the inequalities
$W_a^J S_J\geq 0$ up to resales $U_A\mapsto t U_A$ for non-zero factors $t$, because
there's no nontrivial linear isometry from the simplex to itself besides permutations
of vertices. Therefore, we identity the labal of facets $a$ with the label of 
vertices $A$ and get $V=W^{-1}$. Furthermore, every facet of the original polytope
$\mathcal P$ can be associated with a single $u_A$ going to zero, 
giving a “binary” geometry we will describe later.

(why cluster configuration space, perfect u eqs)

@@

In the last subsection, we have seen that any $n$-dimensional generalized 
permutahedron can be constructed by a Minkowski sum of some simplices labeled by
subsets of $[0,n]$. For a simplex labeled by a subset $I$, it can be realized as the 
Newton Polytope of the linear polynomial $x_I=\sum_{i\in I}x_i$. Therefore, we can
write down a natrual stringy canonical for the generalized permutahedron 
$\mathscr P$
\[
	I_{\mathscr P}(\{S_I\})=\int_{\mathbb R^{n+1}_+}
	\frac{\prod_{i=0}^n \mathrm{d}\log x_i}
	{\operatorname{GL}(1)_+}\prod_{I\in\mathscr P}x_I^{\alpha' S_I},
\]
where the global $\operatorname{GL}(1)_+$ redundance $x_i\mapsto a x_i$ require that 
$\sum_{I\in\mathscr P}S_I = 0$.

Generally, we can consider arbitrary set of subsets of $[0,n]$ in above integrals. 
However, the big polytope of this integral is usually not a simplex.
It's highly non-trivial to figure out all such sets whose big polytopes are simplices,
but we can easily see that every generalized permutahedron satisfies $N=n+m$
because each facet $F_I$ corresponds to a set of nested set $\{[0,n],I\}$ for 
$I\neq [0,n]$.

@@

The following set of equations to define the $n$-dimensional Permutahedron: 
\bea
C_I = (-1)^{|I|} \left( \sum_{i \in I} X_i - \sum _{{i<j}\atop{i,j \in I}} X_{ij} +\cdots + (-1)^{|I|+1}  X_I \right) \nonumber
\eea
for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $X_{I} =0$ for $I=\{ 0,1,\cdots,n \}$.

>>>>

The $\mathcal I(\mathbf X,\{c\})$ is convergent when $\mathbf X$ is contained inside
the Minkowski sum $\mathcal P=\sum_I c_I \mathcal P_I$ of Newton polytopes 
$\mathcal P_I=\mathbf N[p_I]$. For a facet $F_a$ of $\mathcal P$, this condition 
requires that $\mathbf X$ should lay on one side of $F_a$ which is equivalent to 
an inequality of variables $\mathbf S=(X_1,\dots,X_d,-c_1,\dots,-c_m)$, 
$W_a^JS_J\geq 0$, where $W_a^J$ is determined by the facet $F_a$. 
These inequalities cut out a polyhedron in the $(d+m)$-dimensional space of 
$\mathbf S$, which is called the \textit{big polyhedron} of $\mathcal P$, 
and the integral $\mathcal I(\mathbf S)$ converges for each point $\mathbf S$ 
inside this polyhedron.

Dually, we can describe the big polyhedron by its vertices. Suppose 
$\{V_J^A\}_{1\leq A\leq v}$ are its non-zero vertices, the point $\mathbf S$ inside 
the polyhedron can be written as $S_J = U_A V^A_J$ with non-nagetive coefficients 
$\{U_A\}_{1\leq A\leq v}$.  Therefore, the integral $\mathcal I(\mathbf S)$
can be seen as a function of `dual coordinates' $\{U_A\}$ which encourages us to 
rewrite the integral to make it manifest by
\[
	\mathcal I(\mathbf U)=
	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
	\prod_{A}u_A^{\alpha' U_A}
	=
	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
	\prod_{J}p_J^{\alpha' S_J},
\]
where we introduce a new set of variables $u_A = \prod_J p_J^{V_J^A}$ for 
$A=1,\dots,v$. Note that there's no unique way to write $S_J=U_AV_J^A$ when
the big polyhedron is not a simplex, \textit{i.e.} $v>d+m$, and in this case,
$u$-variables $\{u_A\}$ are not independent. 
When the big polyhdron is a simplex, \textit{i.e.} $N=v=d+m$, where $N$ is 
the number of facets of the big polyhdron or the original polytope $\mathcal P$,
and inequalities $U_A=S_J(V^{-1})^J_A\geq 0$ are exactly the inequalities
$W_a^J S_J\geq 0$ up to resales $U_A\mapsto t U_A$ for non-zero factors $t$, because
there's no nontrivial linear isometry from the simplex to itself besides permutations
of vertices. Therefore, we identity the labal of facets $a$ with the label of 
vertices $A$ and get $V=W^{-1}$. Furthermore, every facet of the original polytope
$\mathcal P$ can be associated with a single $u_A$ going to zero, 
giving a ``binary geometry'' we will describe later.

Generally, the big polyhdron of a stringy integral is not necessary to be a simplex.

(cluster configuration space, perfect u eqs)

@@

In the last subsection, we have seen that any $n$-dimensional generalized 
permutahedron can be constructed by a Minkowski sum of some simplices labeled by
subsets of $[0,n]$. For a simplex labeled by a subset $I$, it can be realized as the 
Newton Polytope of the linear polynomial $x_I=\sum_{i\in I}x_i$. Therefore, we can
write down a natrual stringy canonical form for the generalized permutahedron 
$\mathscr P$
\[
	\mathcal I_{\mathscr P}(\{S_I\})=\int_{\mathbb R^{n+1}_+}
	\frac{\prod_{i=0}^n \mathrm{d}\log x_i}
	{\operatorname{GL}(1)_+}\prod_{I\in\mathscr P}x_I^{\alpha' S_I},
\]
where the global $\operatorname{GL}(1)_+$ redundance $x_i\mapsto a x_i$ require that 
$\sum_{I\in\mathscr P}S_I = 0$.

Generally, we can consider arbitrary set of subsets of $[0,n]$ in above integrals. 
However, the big polytope of this integral is usually not a simplex.
It's highly non-trivial to figure out all such sets whose big polytopes are simplices,
but we can easily see that every generalized permutahedron satisfies $N=n+m$
because each facet $F_I$ corresponds to a set of nested set $\{[0,n],I\}$ for 
$I\neq [0,n]$.
Therefore, for a generalized permutahedron $\mathscr P$, we can write the matrix 
$W^J_A$ of facets and get the ABHY conditions $S_J=F_A(W^{-1})^A_J\geq 0$ and 
its $u$-variables $u_A=\prod_J p_J^{(W^{-1})^A_J}$.

@@

($P_n$)

As shown in the last subsection, the $n$-dimensional permutahedron is associated 
with the set of all non-empty subsets of $[0,n]$, which is denoted by $\mathscr P_n$. 
The number of facets of $\mathscr P_n$ is $2^n-2$.

(equations of facets?)

ABHY conditions:
\bea
C_I = (-1)^{|I|} \left( \sum_{i \in I} X_i - \sum _{{i<j}\atop{i,j \in I}} X_{ij} +\cdots + (-1)^{|I|+1}  X_I \right) \nonumber
\eea
for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $X_{I} =0$ for $I=\{ 0,1,\cdots,n \}$.

(proof?)

Then we can then solve for the corresponding $u's$ :
\bea
u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber \\
u^{'}_J &=& \prod_{{0 \in I}\atop{ \{0,\cdots,n\} - I \subset J}} x_I^{(-1)^{|I|-|J|+\color{red}{mod(n, 2)}}} \nonumber
\eea

(notation!)
